Neural models for target-based computer-assisted musical orchestration: a preliminary study

### 2020-05-15 paper/latex/paper.tex

\begin{figure*}
\begin{center}
\includegraphics[scale=0.4]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{center}
\end{figure*}

@@

Some of the targets were made of instrumental samples: a sum of oboe and bassoon notes, single bassoon and bass clarinet notes, two multiphonics of basson and two symphonic chords. The other targets there are: the recordings of two bells, of a car horn, of a gong, of a screaming voice, of a wind harp, of the attack of a brass instrument and the recording of a boat docking.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[scale=0.4]{figs/CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{center}
\end{figure*}

@@

Some of the targets were made of instrumental samples: a sum of oboe and bassoon notes, single bassoon and bass clarinet notes, two multiphonics of bassoon and two symphonic chords. The other targets there are: the recordings of two bells, of a car horn, of a gong, of a screaming voice, of a wind harp, of the attack of a brass instrument and the recording of a boat docking.
